Probability

### 2016-04-21 prob.tex
removed comment
Still cannot prove if projections sum up to projections, they are orthogonal... Decide to leave it there for a while...

\amr{CHECK because sum of
    projections may not be a projection}

\yutsung{I am going to verify if $\proj{\psi_{1}}+\proj{\psi_{2}}$
is a projection, then they are orthogonal. Given any state $\ket{\phi}=a\ket{\psi_{1}}+b\ket{\psi_{2}}$,
if $\proj{\psi_{1}}+\proj{\psi_{2}}$ is a projection, then 
\begin{eqnarray*}
\ket{\phi} & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\ket{\phi}\\
 & = & \left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)\left(a\ket{\psi_{1}}+b\ket{\psi_{2}}\right)\\
 & = & a\ket{\psi_{1}}+b\ket{\psi_{2}}+a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
Therefore, we have 
\begin{eqnarray*}
0 & = & a\ket{\psi_{2}}\ip{\psi_{2}}{\psi_{1}}+b\ket{\psi_{1}}\ip{\psi_{1}}{\psi_{2}}
\end{eqnarray*}
However, $a$ and $b$ can be any numbers. Therefore, we must have
$0=\ip{\psi_{2}}{\psi_{1}}=\ip{\psi_{1}}{\psi_{2}}$.}
\end{itemize}

>>>>

\yutsung{Claim: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then
they are orthogonal. \\
Proof: If $\sum_{i}\proj{\psi_{i}}$ is a projection, then 
\begin{eqnarray*}
\ket{\psi_{j}} & = & \left(\sum_{i}\proj{\psi_{i}}\right)\ket{\psi_{j}}\\
 & = & \sum_{i}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
\end{eqnarray*}
Therefore, we have 
\begin{eqnarray*}
0 & = & \sum_{i\ne j}\ket{\psi_{i}}\ip{\psi_{i}}{\psi_{j}}
\end{eqnarray*}
} 
\end{itemize}
